KV Analysis for Non-Expressive performances

### 2020-05-19 material/analysis/stim_n/duration.Rmd
correc x axis ticks
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

p_duration_seq <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, group = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Non-Expression") +
  scale_x_continuous(breaks=seq(1,66,1)) + scale_y_continuous(breaks=seq(0,2,0.5), limits = c(0, 2))
p_duration_seq
```

>>>>

p_duration_seq <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, group = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Non-Expression") +
  scale_x_continuous(breaks=seq(1,72,1)) + scale_y_continuous(breaks=seq(0,2,0.5), limits = c(0, 2))
p_duration_seq
```

### 2020-05-19 material/analysis/stim_n/ioi_onset.Rmd
correc x axis ticks
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

p_ioi_seq <- ggplot(data = ioi_seq, aes(x = Interval, y = Mean, group = TrialNr)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  facet_grid(SubNr ~ .) +
  labs(x = "Interval", y = "Normalised IOI") + scale_x_continuous(breaks=seq(1,66,1))
p_ioi_seq
```

>>>>

p_ioi_seq <- ggplot(data = ioi_seq, aes(x = Interval, y = Mean, group = TrialNr)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  facet_grid(SubNr ~ .) +
  labs(x = "Interval", y = "Normalised IOI") + scale_x_continuous(breaks=seq(1,71,1))
p_ioi_seq
```

### 2020-05-19 material/analysis/stim_n/kv.Rmd
correc x axis ticks
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

p_kv_seq <- ggplot(data = kv_seq, aes(x = RowNr, y = Mean, group = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Key Velocity") + scale_x_continuous(breaks=seq(1,66,1))
p_kv_seq
```

>>>>

p_kv_seq <- ggplot(data = kv_seq, aes(x = RowNr, y = Mean, group = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Key Velocity") + scale_x_continuous(breaks=seq(1,72,1))
p_kv_seq
```
